### 2020-11-15 Thesis-Chapter3-PolicyMaking.tex
Clean up arguments chapter notes
Add OODA process clear out old DFDs

@@

\begin{figure}[h]
    \centering\CaptionFontSize
    \includegraphics[width=\linewidth]{dfds/build/OODA-loop.png}
    \caption[The OODA Loop for Wicked Problems]{The OODA Loop for Wicked Problems}
    \label{fig-policy-ooda-loop}
\end{figure}

@@

Traditional policymaking typically follows either a rational approach rooted in the scientific method, aiming to be
thorough and complete, or an intuitional approach rooted in evolutionary trial and error, humbly aiming only to take
steps in the right direction. Both approaches have their strengths, but neither is suited to the complex and
controversial nature of so-called ``\acp{wicked-prob}.'' The strategy proposed here relies on the goodwill participation
of all parties, who engage in ongoing research and debate that rejects easy answers, encourages flexible risk-based
solutions, and crystallizes discussion around specific proposals. \Acp{argmap} are one tool that may facilitate this
process. The result from a single iteration is an imperfect step forward based on implementing a particular proposal.
The result from many iterations is the breakdown of the problem into sub-problems---some tame and inevitably some still
wicked. The tame sub-problems can be addressed with the \ac{classical-method}, and the wicked sub-problems, by now
restrained under a sound and agreeable strategy, can be addressed with \ac{incrementalism}.

>>>>

% FIXME: include this idea somewhere in this section.
% Note: a problem with muddling through wicked problems is that each attempted fix leads to long lasting unintended side
% effects. This is especially true with matters of encryption, where the data could be stored for years till it can be
% decrypted! So must be very careful to avoid solution attempts that leave long scars.

@@

\begin{figure}[h]
    \centering\CaptionFontSize
    \includegraphics[width=\linewidth]{dfds/build/OODA-loop.png}
    \caption{The OODA Loop for Wicked Problems}
    \label{fig-policy-ooda-loop}
\end{figure}

@@

Traditional policymaking typically follows either a rational approach rooted in the scientific method, aiming to be
thorough and complete, or an intuitional approach rooted in evolutionary trial and error, humbly aiming only to take
steps in the right direction. Both approaches have their strengths, but neither is suited to the complex and
controversial nature of so-called ``\acp{wicked-prob}.'' The strategy proposed here relies on the goodwill participation
of all parties, who engage in ongoing research and debate that rejects easy answers, encourages flexible risk-based
solutions, and crystallizes discussion around specific proposals. \Acp{argmap} are one tool that may facilitate this
process. The result from a single iteration is an imperfect step forward based on implementing a particular proposal.
The result from many iterations is the breakdown of the problem into sub-problems---some tame and inevitably some still
wicked. The tame sub-problems can be addressed with the \ac{classical-method}, and the wicked sub-problems, by now
restrained under a sound and agreeable strategy, can be addressed with \ac{incrementalism}. This process is demonstrated
in \myfig{fig-policy-ooda-process}.

\begin{figure}[h]
  \centering\CaptionFontSize
  \includegraphics[width=\linewidth]{dfds/build/OODA-policy-process.png}
  \caption{Using the \ac{OODAloop} to Tackle Wicked Problems}
  \label{fig-policy-ooda-process}
\end{figure}
